---
title: '01 Prep - `r unlist(strsplit(getwd(), "/"))[7]` - `r unlist(strsplit(getwd(), "/"))[8]`'
author:
  - name: "Emir Turkes [emir.turkes@eturkes.com]"
  - name: "UK Dementia Research Institute at UCL"
date: '`r strftime(Sys.time(), "%B %d, %Y")`'
bibliography: '../../../../`r unlist(strsplit(getwd(), "/"))[4]`.bib'
link-citations: true
output:
  html_document:
    code_folding: hide
    number_sections: true
    theme: lumen
    highlight: haddock
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding, output_file = file.path(
      "..", "..", "..",
      "..", "results", unlist(strsplit(getwd(), "/"))[6],
      unlist(strsplit(getwd(), "/"))[7], unlist(strsplit(getwd(), "/"))[8], "01_prep.html"
  ))})
---

<style type="text/css">
body {font-size: 16px;}
h1.title {font-size: 35px;}
h1 {font-size: 24px;}
h2 {font-size: 22px;}
h3 {font-size: 20px;}
.toc-content {padding-left: 0px; padding-right: 0px;}
div.tocify {width: 100%;}
.tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 25px; text-indent: 0;}
.tocify-subheader .tocify-subheader .tocify-item {font-size: 0.95em; padding-left: 35px; text-indent: 0;}
div.main-container {max-width: none; width: 95%;}
</style>

*This file is a part of the [Pathology Signatures Project](https://github.com/eturkes/pathology-signatures).*

In this document we prepare the gene count matrix for downstream analysis.
The data here is derived from @`r unlist(strsplit(getwd(), "/"))[7]` and will be referenced using the name ``r unlist(strsplit(getwd(), "/"))[7]``.
This analysis focuses on neurons bearing neurofibrillary tangles (NFTs) from the dataset.

```{r}
# Some standard boilerplate.
# --------------------------
#    This file is part of pathology-signatures.
#    Copyright (C) 2022  Emir Turkes, UK DRI at UCL
#
#    This program is free software: you can redistribute it and/or modify
#    it under the terms of the GNU General Public License as published by
#    the Free Software Foundation, either version 3 of the License, or
#    (at your option) any later version.
#
#    This program is distributed in the hope that it will be useful,
#    but WITHOUT ANY WARRANTY; without even the implied warranty of
#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#    GNU General Public License for more details.
#
#    You should have received a copy of the GNU General Public License
#    along with this program.  If not, see <http://www.gnu.org/licenses/>.
#
#    Emir Turkes can be contacted at emir.turkes@eturkes.com

packages <- c("conflicted")
invisible(suppressPackageStartupMessages(lapply(packages, library, character.only = TRUE)))

protocol <- c("human", "droplet", "single-cell", "umis") # See `cluster_pipeline` in `utils.R`.
group <- unlist(strsplit(getwd(), "/"))[8] # Extract group.
vars_to_regress <- NULL # See `cluster_pipeline` in `utils.R`.
parallel_override <- NULL # See `parallel_plan` in `utils.R`.

# Metadata to plot after dimensionality reduction and clustering.
# Values in list can include "no_legend and/or "no_label" to exclude those.
# -------------------------------------------------------------------------
metadata_to_plot <- vector("list", 3)
names(metadata_to_plot) <- c("seurat_clusters", "donor", "Phase")
metadata_to_plot$donor <- "no_label"
metadata_to_plot$Phase <- "no_label"
# -------------------------------------------------------------------------

data_name <- unlist(strsplit(getwd(), "/"))[6]
analysis_no <- 1
assets_dir <- file.path("..", "..", "..", "..", "assets") # Backed up files and data.
results_dir <- file.path(
  "..", "..", "..", "..", "results", data_name, unlist(strsplit(getwd(), "/"))[7], paste0("0", analysis_no)
)

cache_dir <- file.path(
  "..", "..", "..", "..", "cache", data_name, unlist(strsplit(getwd(), "/"))[7], paste0("0", analysis_no)
)
if (!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

knitr::opts_chunk$set(fig.width = 10, fig.height = 7, dpi = 300)
# --------------------------
```

# References

This is the concluding section of the document.
Here we output the `sessionInfo` and create a bibliography for works cited.

```{r}
sessionInfo()
```
